MP MetaAnalysis

### 2018-06-28 Paper_Analyses.Rmd
final ICIS 2018 poster

@@

# Plotting defaults

@@

## Main Mispronunciation Sensitivity Effects

@@

## Main Mispronunciation Sensitivity Effects with Age Moderators

@@

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 600, height = 400, units = "px")

@@

## Correlation MP effect and Vocabulary

@@

## Number of Features Changed

@@

db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)

summary(rma_NFeatures)

@@

@@

@@

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeatures_agesub)

@@

### Number of features with condition moderator

```{r NFeaturesCondition}

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeatures)

### Number of features with age moderator

db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)

summary(rma_NFeaturesAge)
```

### Number of features with condition and age moderators

```{r NFeaturesCondition_age}

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeaturesAge)
```

### Features changed with age moderator, subset to same age range

```{r FeatureAgeRangeSubset}

@@

rma_FeatureAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)

summary(rma_FeatureAgeS)

#rma_FeatureS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)

#summary(rma_FeatureS)

@@

dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "one",
                         ifelse(dat_f$n_feature == 2, "two",
                                ifelse(dat_f$n_feature == 3, "three",
                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))

@@

p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = feat_cat)) + 
  geom_point(aes(size = weights_g, shape = feat_cat),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat.jpg", p)

```
### Plot number of Features subsetted for age

```{r PlotFeatEffect_agesubset}

dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
                         ifelse(dat_fage$n_feature == 2, "2-feature",
                                ifelse(dat_fage$n_feature == 3, "3-feature",
                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))

dat_fage <- subset(dat_fage, feat_cat != "none")

dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

@@

p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
  geom_point(aes(size = weights_g, shape = Features_changed),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
    scale_colour_manual(values=cbPalette)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat_agesub.jpg", p)

@@

### Plot number of Features subsetted for age Boxplot

```{r PlotFeatEffect_agesubset_boxplot}

dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
                         ifelse(dat_fage$n_feature == 2, "2-feature",
                                ifelse(dat_fage$n_feature == 3, "3-feature",
                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))

dat_fage <- subset(dat_fage, feat_cat != "none")

dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

p <- ggplot(dat_fage, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

ggsave("figures/AgeEffect_log_feat_agesub_noage.jpg", p)

### Type of MP: Vowel, consonant, or tone

summary(rma_TypeFeaturesMP)

### Type of MP: Vowel, consonant, or tone with age moderator

rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesMPAge)
```

```{r MPtypeCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)

summary(rma_TypeFeatures)

### Type of MP: Vowel, consonant, or tone with age and condition moderator

```{r MPtypeCondition_age}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesAge)
```

### Type of MP with language family moderator

```{r MPtypeLanguage}
#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
#                type_feature == "tone")

dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")

dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)

summary(rma_TypeFeatures_Lang)
```

### Type of MP with language family and condition moderators

```{r MPtypeLanguageCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
                #type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)

### Plot MP type: Consonant, Vowel, or Tone?

```{r PlotCVEffect}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
  facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_CV.jpg", p)
```

p <- ggplot(dat_type_sub, aes(type_feature, g_calc, color = type_feature)) + 
  geom_boxplot() + 
  facet_grid(lang_family~condition_label)+
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Language Family") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/LangFamily_CV.jpg", p)
```

@@

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

@@

@@

@@

@@

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

summary(rma_DistractorAge)

@@

summary(rma_DistractorAge)

@@

@@

@@

@@

@@

@@

```{r PlotDistFamEffect}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
  facet_grid(.~dist_code)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)

@@

### Plot Distractor Familiarity (w/o age)

```{r PlotDistFamEffect_NoAge}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(dist_code, g_calc, color = condition_label)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Distractor Familiarity") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/Distractor_fam_log.jpg", p)

### Plot Distractor Familiarity (w/o age, subset to age range)

@@

@@

dat_age= dat%>%
  filter(mean_age_1>min_age&mean_age_1<max_age)

dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "mispronunciation")
dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")

@@

ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)

@@

### Plot Distractor Familiarity by age subsetted for age

```{r PlotDistFam}

@@

dat_fage= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$dist_fam <- ifelse(dat_fage$object_pair == "familiar_novel", "Novel Distractor", "Familiar Distractor")

p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_fam),show.legend=FALSE) + 
  facet_grid(.~dist_fam)+
    scale_colour_manual(values=cbPalette)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_DistFam_agesub.jpg", p)

@@

>>>>

# assign language families

db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

@@

Plotting defaults

@@

## Condition: Mispronunciation Sensitivity Effects

@@

## Age: Mispronunciation Sensitivity Effects with Age Moderators

@@

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 500, height = 300, units = "px")

@@

## Vocabulary size: Correlation between mispronunciation sensitivity and vocabulary

@@

## Size of Mispronunciation: Measured in Features Changed

@@

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)

summary(rma_NFeatures)
aov.feat <- anova(rma_NFeatures)

n_feat <- round(coef(summary(rma_NFeatures))[2,], 2)

@@

The moderator test was significant:
`print(aov.feat)`

Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

### Number of features with age moderator interaction

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)

summary(rma_NFeatures)
aov.feat <- anova(rma_NFeatures)

n_feat <- round(coef(summary(rma_NFeatures))[4,], 2)

The moderator test was significant:
`print(aov.feat)`

But there was no significant interaction between number of features changed and age:

Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

Number of features is still significant

@@

#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)

#summary(rma_NFeatures_agesub)

@@

### Number of features with age moderator subset to age range
Size of mispronunciation, measured in features changed

No interaction between features and age

```{r NFeatures_subset_age}

@@

#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_f, random = ~collapse | short_cite)

#summary(rma_NFeatures_agesub)

@@

# mf <- subset(dat_f, n_feature == "3")
# min_age <- min(mf$mean_age_1)
# max_age <- max(mf$mean_age_1)
# 
# dat_fage= dat_f%>%
#   filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
                         ifelse(dat_f$n_feature == 2, "2-feature",
                                ifelse(dat_f$n_feature == 3, "3-feature",
                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))

@@

dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

@@

p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Number_of_Features.jpg", 
       width = 500, height = 300, units = "px")

@@

@@

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

#summary(rma_Distractor)

aov.type <- anova(rma_Distractor)

sum_eff <- round(coef(summary(rma_TypeFeatures_Lang))[2,], 2)

@@

The moderator test was not significant:
`print(aov.type)`

No significant interaction between feature type and language family:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

aov.type <- anova(rma_Distractor)

sum_eff <- round(coef(summary(rma_Distractor))[4,], 2)

@@

The moderator test was significant:
`print(aov.type)`

But there was no significant interaction between distractor familiarity and condition:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

#summary(rma_DistractorAge)

aov.type <- anova(rma_DistractorAge)

sum_eff <- round(coef(summary(rma_DistractorAge))[4,], 2)

```
The moderator test was not significant:
`print(aov.type)`

There was no significant interaction between distractor familiarity and age:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

summary(rma_DistractorAge)  
aov.type <- anova(rma_DistractorAge)

sum_eff <- round(coef(summary(rma_DistractorAge))[7,], 2)

@@

The moderator test was significant:
`print(aov.type)`

There was a significant interaction between distractor familiarity and condition, but not age:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

### Distractor Familiarity, subset to same age range

fn <- subset(dat, object_pair=="familiar_novel")
min_fn <- min(mf$mean_age_1)
max_fn <- max(mf$mean_age_1)

ff <- subset(dat, object_pair=="familiar_familiar")
min_ff <- min(ff$mean_age_1)
max_ff <- max(ff$mean_age_1)

min_age <- pmax(min_fn, min_ff)
max_age <- pmin(max_fn, max_ff)

dat_age= db_ET_MP%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)

#summary(rma_Distractor)

aov.type <- anova(rma_Distractor)

sum_eff <- round(coef(summary(rma_Distractor))[2,], 2)

The moderator test was not significant:
`print(aov.type)`

There was no significant effect of distractor familiarity:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

fn <- subset(dat, object_pair=="familiar_novel")
min_fn <- min(mf$mean_age_1)
max_fn <- max(mf$mean_age_1)

ff <- subset(dat, object_pair=="familiar_familiar")
min_ff <- min(ff$mean_age_1)
max_ff <- max(ff$mean_age_1)

min_age <- pmax(min_fn, min_ff)
max_age <- pmin(max_fn, max_ff)

@@

The moderator test was significant:
`print(aov.type)`

There was a significant interaction between distractor familiarity and condition:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

#summary(rma_DistractorAgeS)

aov.type <- anova(rma_Distractor)

sum_eff <- round(coef(summary(rma_Distractor))[8,], 2)

@@

The moderator test was significant:
`print(aov.type)`

There was no significant interaction between distractor familiarity, condition, and age:

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")

p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_boxplot() + 
  facet_grid(.~dist_code) +
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Distractor_fam.jpg", 
       width = 500, height = 300, units = "px")

@@

@@

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")

@@

@@

  jpeg(filename = "figures/Distractor_fam_age_AgeSubset.jpg", 
       width = 500, height = 300, units = "px")

@@

### Plot Distractor Familiarity by age (subset to same age range)

```{r PlotDistFamEffect_age}

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

@@

p <- ggplot(dat_age, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
  facet_grid(.~dist_code)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=cbPalette)+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

  jpeg(filename = "figures/Distractor_fam_AgeSubset.jpg", 
       width = 500, height = 300, units = "px")

@@

### Type of MP: Vowel, consonant, or tone role in object identification

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

#summary(rma_TypeFeaturesMP)

aov.type <- anova(rma_TypeFeaturesMP)

type_feat <- round(coef(summary(rma_TypeFeaturesMP))[2,], 2)

The moderator test was not significant:
`print(aov.type)`

No significant effect of feature type:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Type of MP: Vowel, consonant, or tone role in object identification with age moderator

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)

#summary(rma_TypeFeaturesMPage)

aov.type <- anova(rma_TypeFeaturesMPage)

type_feat <- round(coef(summary(rma_TypeFeaturesMPage))[4,], 2)

The moderator test was not significant:
`print(aov.type)`

No significant effect of feature type:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Type of MP: Vowel, consonant, or tone role in object identification with language family moderator

```{r MPtype_lang}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

dat_type_sub <- subset(db_MP_type, lang_family != "Sino-Tibetian")

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family, data = dat_type_sub, random = ~collapse | short_cite)

#summary(rma_TypeFeatures_Lang)

aov.type <- anova(rma_TypeFeatures_Lang)

type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[4,], 2)

```
The moderator test was not significant:
`print(aov.type)`

No significant interaction between feature type and language family:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

```{r MPtype_cond}
db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
#db_type <- subset(dat, type_feature != "consonant_and_vowel")

rma_TypeFeaturesMPcond <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)

#summary(rma_TypeFeaturesMPcond)

aov.type <- anova(rma_TypeFeaturesMPcond)

type_feat <- round(coef(summary(rma_TypeFeaturesMPcond))[2,], 2)

The moderator test was not significant:
`print(aov.type)`

No significant interaction between feature type and condition:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Type of MP: Vowel, consonant, or tone with condition and age moderators

```{r MPtype_cond_age}
db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
#db_type <- subset(dat, type_feature != "consonant_and_vowel")

rma_TypeFeaturesMPcondage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesMPcondage)

aov.type <- anova(rma_TypeFeaturesMPcondage)

type_feat <- round(coef(summary(rma_TypeFeaturesMPcondage))[8,], 2)

The moderator test was significant:
`print(aov.type)`

There was a significant interaction between feature type, condition, and age:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Type of MP: Vowel, consonant, or tone with language family and condition moderators

```{r MPtype_cond_lang}
db_MP_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

dat_type_sub <- subset(db_MP_type, lang_family != "Sino-Tibetian")

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)

aov.type <- anova(rma_TypeFeatures_Lang)

type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)

The moderator test was significant:
`print(aov.type)`

There was a significant interaction between feature type, language family, and condition:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Type of MP: Vowel, consonant, or tone with language family, condition, and age moderators

```{r MPtype_cond_lang}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition*age.C, data = dat_type_sub, random = ~collapse | short_cite)

aov.type <- anova(rma_TypeFeatures_Lang)

type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)

```
The moderator test was significant:
`print(aov.type)`

There was a significant interaction between feature type, age, and language family, and condition:

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Plot MP type: feature type, condition, and age

```{r PlotCVEffect_cond_age}

dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

#dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")

dat_type$condition_label = ifelse(dat_type$condition==1, "Correct", "Mispronunciation")

p <- ggplot(dat_type, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
    facet_grid(.~type_feature)+
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/FeatureType_Cond_Age.jpg", 
       width = 500, height = 300, units = "px")

dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")

#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")

dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
